Analysis

### 2017-03-23 Analysis.Rmd
Cleanup graphs

## Leaf Sheath Blight Severity Model
```{r}
(LShB_lmm_2015 <- lmer(LShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
                       data = AUDPS_2015))
summary(LShB_lmm_2015)

>>>>

## Leaf Sheath Blight Severity Model
```{r}
(LShB_lmm_2015 <- glmer(LShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
                          family = binomial(link = "logit"), data = AUDPS_2015))
summary(LShB_lmm_2015)
